---
title: "05-exercises"
author: "Zhihui Zhang"
date: "2016-05-08"
output: html_document
---

## Reading:
- **APM** Chapter 8.1-8.5 "Regression Trees and Rule-Based Models" (25 pages)
- **APM** Chapter 14.1-14.5 "Classification Trees and Rule-Based"  

```{r, echo=FALSE, results='hide', warning=FALSE }
packs <-  c('ggplot2', 'magrittr', 'dplyr', 'caret', 'AppliedPredictiveModeling', 'MASS', 'maptree')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

.. = NULL  # For Aesthetics

```


## Exercise 1: GermanCredit

Revisit the GermanCredit data. Use `caret` to build models of `Class` using the following techniques:

- glm
- rpart
- knn
- party::ctree
- randomForest
- A method of your choice from the Caret Model List (you will need to install any dependencies)

Save the caret objects with the names provided.

```{r}

data("GermanCredit")
gc <- GermanCredit
set.seed(10)
ctrl <- trainControl(method='boot', number=5, classProb=TRUE, savePrediction=TRUE)

fit.glm <- train(Class ~ ., data=gc, method="glm", family="binomial", trControl=ctrl)
fit.glm$finalModel  %>% summary()

fit.knn <- train(Class ~ ., data=gc, method="knn", trControl=ctrl, tuneGrid=data.frame(k=c(40,50,60)))
fit.knn$finalModel %>% summary()

fit.rpart <- train(Class ~ ., data=gc, trControl=ctrl, method="rpart", tuneLength=20)
fit.rpart$finalModel %>% summary()
fit.rpart$finalModel %>% draw.tree(nodeinfo = T)

fit.rf <- train(Class ~ ., data=gc, trControl=ctrl, method="rf")
fit.rf$finalModel %>% summary()

fit.svmRadial <- train(Class ~ ., data=gc, trControl=ctrl, method="svmRadial")
fit.svmRadial$finalModel %>% summary()


```


- Compare the models using `caret::confusionMatrix`
- Comparing the models Using the `pROC` packages
  - create ROC curves for the models 
  
Show your work! 

```{r}

cm.glm <- fit.glm %>% confusionMatrix( positive="Bad")
cm.knn <- fit.knn %>% confusionMatrix( positive="Bad")
cm.rpart <- fit.rpart %>% confusionMatrix( positive="Bad")
cm.rf <- fit.rf %>% confusionMatrix( positive="Bad")
cm.svmRadial <- fit.svmRadial %>% confusionMatrix( positive="Bad")

table(fit.glm$pred$pred, fit.glm$pred$obs) %>% confusionMatrix()
table(fit.knn$pred$pred, fit.knn$pred$obs) %>% confusionMatrix()
table(fit.rpart$pred$pred, fit.rpart$pred$obs) %>% confusionMatrix()
table(fit.rf$pred$pred, fit.rf$pred$obs) %>% confusionMatrix()
table(fit.svmRadial$pred$pred, fit.svmRadial$pred$obs) %>% confusionMatrix()

roc.glm <- roc(fit.glm$pred$obs, fit.glm$pred$Bad, auc=TRUE )
roc.glm %>% plot( print.auc=TRUE, grid=TRUE)

roc.knn <- roc(fit.knn$pred$obs, fit.knn$pred$Bad, auc=TRUE )
roc.knn %>% plot( print.auc=TRUE, grid=TRUE)

roc.rpart <- roc(fit.rpart$pred$obs, fit.rpart$pred$Bad, auc=TRUE )
roc.rpart %>% plot( print.auc=TRUE, grid=TRUE)

roc.rf <- roc(fit.rf$pred$obs, fit.rf$pred$Bad, auc=TRUE )
roc.rf %>% plot( print.auc=TRUE, grid=TRUE)

roc.svmRadial <- roc(fit.svmRadial$pred$obs, fit.svmRadial$pred$Bad, auc=TRUE )
roc.svmRadial %>% plot( print.auc=TRUE, grid=TRUE)

```


Q: Which models would you select based on these tools?

Q: If you assume that a `Class=="bad""` is 10 more costly than `Class=="good"`, determine your threshold for the model of your choice.  Show your work.

Among the models that showed higher accuracy than the naiive guess, Radom Forest Model shows the highest accuracy and lowest cost, thus it's probably the best model.

```{r}
#PCF = (P × C(+|−)) / (P × C(−|+) + (1 − P) × C(+|−))
#normalized expected cost (NEC) function to characterize the model
#NEC = PCF × (1 − TP) + (1 − PCF) × FP
pcf <- function(p, cfalse, ctrue) { p* ctrue / (p*cfalse + (1-p)*ctrue)}
ncf <- function(pcf, tp, fp) { pcf * (1-tp) + (1-pcf) * fp}

pcf.gc <- pcf(0.3, 10, 1)
pcf.gc

ncf.glm <- ncf(pcf.gc, cm.glm$table[2,1], cm.glm$table[1,2])
ncf.glm

ncf.knn <- ncf(pcf.gc, cm.knn$table[2,1], cm.knn$table[1,2])
ncf.knn

ncf.rpart <- ncf(pcf.gc, cm.rpart$table[2,1], cm.rpart$table[1,2])
ncf.rpart

ncf.rf <- ncf(pcf.gc, cm.rf$table[2,1], cm.rf$table[1,2])
ncf.rf

ncf.svmRadial <- ncf(pcf.gc, cm.svmRadial$table[2,1], cm.svmRadial$table[1,2])
ncf.svmRadial

```

